Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Center figure

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 95th percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
width="14.82cm"}

@@

cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/bioregion_cluster_regression_coefficients.csv"), DataFrame)
cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])

@@

## ADRIA - CoralBlox

>>>>

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 95th percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
fig-align="center" width="14.82cm"}

@@

cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])

@@

## ADRIA-CoralBlox
